### 2024-05-01 Tables/MD_noMD_readmort_fullsample.tex
Add Table files
make tables/figures look better and more consistent

\begin{table}[htbp]
   \caption{\label{tab:MD_noMD_fullsample} Comparison of MD vs. non-MD Nonprofit Readmissions and Mortality Regression Results}
   \bigskip
   \centering
   \begin{tabular}{lcc}
      \toprule
                                        & Weighted Avg. Readmission Rate & Weighted Avg. Mortality Rate\\  
                                        & (1)                            & (2)\\  
      \midrule 
      NP w/ MD Executive x Post Penalty & -0.40$^{***}$                  & -0.19\\   
                                        & (0.14)                         & (0.15)\\   
      \textbf{Comparison Group:}        &                                & \\  
      NP w/out MD Executive             & $\checkmark$                   & $\checkmark$\\   
       \\
      Observations                      & 2,471                          & 2,462\\  
      \bottomrule
   \end{tabular}
\end{table}

>>>>

\begin{table}[ht!]
   \caption{\label{tab:MD_noMD_readmort_fullsample} Non-MD vs. MD Executive Readmission and Mortality Regression Results}
   \bigskip
   \centering
   \begin{tabular}{lcc}
      \toprule
                                       & Weighted Avg. Readmission Rate & Weighted Avg. Mortality Rate\\  
                                       & (1)                            & (2)\\  
      \midrule 
      NP w/out MD Exec x Post Programs & -0.40$^{***}$                  & -0.19\\   
                                       & (0.14)                         & (0.15)\\   
      \textbf{Comparison Group:}       &                                & \\  
      NP w/ MD Exec                    & $\checkmark$                   & $\checkmark$\\   
       \\
      Observations                     & 2,471                          & 2,462\\  
      \bottomrule
   \end{tabular}

   \par \raggedright 
   Results from Equation \ref{eq:clinical} with readmission and mortality rates as outcome variables.\\
   Standard errors are clustered at the hospital level.\\
   Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1
\end{table}

### 2024-05-01 Tables/MD_noMD_readmort_synth.tex
add tables and update descriptive graph to include for-profits
make tables/figures look better and more consistent

\caption{Comparison of MD vs. non-MD Nonprofit Readmissions and Mortality Synthetic DiD Results}
\centering
\begin{tabular}[t]{lcc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{Weighted Avg. Readmission Rate} & \multicolumn{1}{c}{Weighted Avg. Mortality Rate} \\
 & (1) & (2)\\
\midrule
NP w/ MD Executive x Post Penalty & -0.28$^{*}$ & -0.19\\
 & (0.12) & (0.11)\\
\textbf{Comparison Group:} &  & \\
NP w/out MD Executive & $\checkmark$ & $\checkmark$\\
\\
Observations & 2,335 & 2,325\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:MD_noMD_readmort_synth}Non-MD vs. MD Executive Readmission and Mortality Synthetic DiD Results}
\centering
\begin{tabular}[t]{lcc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{Weighted Avg. Readmission Rate} & \multicolumn{1}{c}{Weighted Avg. Mortality Rate} \\
 & (1) & (2)\\
\midrule
NP w/out MD Exec x Post Program & -0.28$^{*}$ & -0.19\\
 & (0.13) & (0.11)\\
\textbf{Comparison Group:} &  & \\
NP w/ MD Exec & $\checkmark$ & $\checkmark$\\
 &  & \\
\addlinespace
Observations & 2,335 & 2,325\\
\bottomrule
\multicolumn{3}{l}{\textsuperscript{} Results from Equation with readmission and mortality rates as}\\
\multicolumn{3}{l}{outcome variables.}\\
\multicolumn{3}{l}{\textsuperscript{} Standard errors are clustered at the hospital level.}\\
\multicolumn{3}{l}{\textsuperscript{} Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1}\\
\end{tabular}
\end{table}

### 2024-05-01 Tables/MD_noMD_uncompCMI_fullsample.tex
Add Table files
update tables
make tables/figures look better and more consistent

\begin{table}[htbp]
   \caption{\label{tab:MD_noMD_uncomp_CMI_fullsample} Comparison of MD vs. non-MD Nonprofit Uncompensated Care and CMI Regression Results}
   \bigskip
   \centering
   \begin{tabular}{lcc}
      \toprule
                                        & Uncomp. Care (Millions) & Case Mix Index\\  
                                        & (1)                     & (2)\\  
      \midrule 
      NP w/ MD Executive x Post Penalty & -4.46                   & 0.03$^{***}$\\   
                                        & (10.39)                 & (0.01)\\   
      \textbf{Comparison Group:}        &                         & \\  
      NP w/out MD Executive             & $\checkmark$            & $\checkmark$\\   
       \\
      Observations                      & 1,440                   & 1,654\\  
      \bottomrule
   \end{tabular}
\end{table}

>>>>

\begin{table}[ht!]
   \caption{\label{tab:MD_noMD_uncompCMI_fullsample} Non-MD vs. MD Executive Uncompensated Care and CMI Regression Results}
   \bigskip
   \centering
   \begin{tabular}{lcc}
      \toprule
                                       & Uncompensated Care & Case Mix Index\\  
                                       & (1)                & (2)\\  
      \midrule 
      NP w/out MD Exec x Post Programs & 0.01               & 0.03$^{***}$\\   
                                       & (0.01)             & (0.01)\\   
      \textbf{Comparison Group:}       &                    & \\  
      NP w/ MD Executive               & $\checkmark$       & $\checkmark$\\   
       \\
      Observations                     & 1,440              & 1,654\\  
      \bottomrule
   \end{tabular}

   \par \raggedright 
   Results from Equation \ref{eq:forprofit} with readmission and mortality rates as outcome variables.\\
   Standard errors are clustered at the hospital level.\\
   Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1\\
   Uncompensated care measured as percent of total operating expenses.
\end{table}

### 2024-05-01 Tables/MD_noMD_uncompCMI_synth.tex
Add Table files
make tables/figures look better and more consistent

\caption{\label{tab:MD_noMD_uncompCMI_synth}Comparison of MD vs. non-MD Nonprofit Uncompensated Care and CMI Synthetic DiD Results}
\centering
\begin{tabular}[t]{lcc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{Uncomp. Care (Millions)} & \multicolumn{1}{c}{Case Mix Index} \\
\cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3}
 & (1) & (2)\\
\midrule
NP w/ MD Executive x Post Penalty & 3.12 & 0.03$^{**}$\\
 & (3.04) & (0.01)\\
\textbf{Comparison Group:} &  & \\
NP w/out MD Executive & $\checkmark$ & $\checkmark$\\
Observations & 625 & 1635\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:MD_noMD_uncompCMI_synth}Non-MD vs. MD Executive Uncompensated Care and CMI Synthetic DiD Results}
\centering
\begin{tabular}[t]{lcc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{Uncompensated Care} & \multicolumn{1}{c}{Case Mix Index} \\
 & (1) & (2)\\
\midrule
NP w/out MD Exec x Post Programs & 0.02$^{*}$ & 0.03$^{***}$\\
 & (0.01) & (0.01)\\
\textbf{Comparison Group:} &  & \\
NP w/ MD Exec & $\checkmark$ & $\checkmark$\\
 &  & \\
\addlinespace
Observations & 15,585 & 2,900\\
\bottomrule
\multicolumn{3}{l}{\textsuperscript{} Results from Equation with readmission and mortality rates as outcome}\\
\multicolumn{3}{l}{variables.}\\
\multicolumn{3}{l}{\textsuperscript{} Standard errors are clustered at the hospital level.}\\
\multicolumn{3}{l}{\textsuperscript{} Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1}\\
\multicolumn{3}{l}{\textsuperscript{} Uncompensated care measured as percent of total operating expenses.}\\
\end{tabular}
\end{table}

### 2024-05-01 Tables/forprofit_readmort_synth.tex
add tables and update descriptive graph to include for-profits
make tables/figures look better and more consistent

\caption{\label{tab:forprofit_uncompCMI_synth} Comparison to For-Profit Uncompensated Care and CMI Synthetic DiD Results}
\centering
\begin{tabular}[t]{lcccccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Uncomp. Care (Millions)} & \multicolumn{3}{c}{Case Mix Index} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7}
 & (1) & (2) & (3) & (1) & (2) & (3)\\
\midrule
For Profit x Post Penalty & 10.52$^{***}$ & 11.69$^{***}$ & 7.6$^{*}$ & 0 & 0.02$^{*}$ & 0\\
 & (2.34) & (2.5) & (3.07) & (0.01) & (0.01) & (0.01)\\
\textbf{Comparison Group:} &  &  &  &  &  & \\
All Nonprofits & $\checkmark$ &  &  & $\checkmark$ &  & \\
Nonprofits w/ MD &  & $\checkmark$ &  &  & $\checkmark$ & \\
\addlinespace
Nonprofits w/out MD &  &  & $\checkmark$ &  &  & $\checkmark$\\
Observations & 4940 & 1330 & 1815 & 12320 & 2880 & 4065\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:forprofit_readmort_synth}Comparison to For-Profit Readmission and Mortality Synthetic DiD Results}
\centering
\begin{tabular}[t]{l>{\centering\arraybackslash}p{.2textwidth}>{\centering\arraybackslash}p{.2textwidth}>{\centering\arraybackslash}p{.2textwidth}>{\centering\arraybackslash}p{.2textwidth}>{\centering\arraybackslash}p{.2textwidth}>{\centering\arraybackslash}p{.2textwidth}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Weighted Avg. Readmission Rate} & \multicolumn{3}{c}{Weighted Avg. Mortality Rate} \\
 & (1) & (2) & (3) & (1) & (2) & (3)\\
\midrule
For Profit x Post Programs & -0.07 & -0.32$^{*}$ & -0.03 & -0.01 & -0.17 & 0.02\\
 & (0.04) & (0.12) & (0.06) & (0.04) & (0.11) & (0.06)\\
\textbf{Comparison Group:} &  &  &  &  &  & \\
All Nonprofits & $\checkmark$ &  &  & $\checkmark$ &  & \\
Nonprofits w/ MD &  & $\checkmark$ &  &  & $\checkmark$ & \\
\addlinespace
Nonprofits w/out MD &  &  & $\checkmark$ &  &  & $\checkmark$\\
 &  &  &  &  &  & \\
Observations & 15,585 & 2,900 & 4,705 & 15,505 & 2,895 & 4,690\\
\bottomrule
\multicolumn{7}{l}{\textsuperscript{} Results from Equation with readmission and mortality rates as outcome variables.}\\
\multicolumn{7}{l}{\textsuperscript{} Standard errors are clustered at the hospital level.}\\
\multicolumn{7}{l}{\textsuperscript{} Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1}\\
\end{tabular}
\end{table}

### 2024-05-01 Tables/forprofit_uncompCMI_synth.tex
Add Table files
make tables/figures look better and more consistent

\caption{\label{tab:forprofit_uncompCMI_synth} Comparison to For-Profit Uncompensated Care and CMI Synthetic DiD Results}
\centering
\begin{tabular}[t]{lcccccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Uncomp. Care (Millions)} & \multicolumn{3}{c}{Case Mix Index} \\
 & (1) & (2) & (3) & (1) & (2) & (3)\\
\midrule
For Profit x Post Penalty & 10.53$^{***}$ & 11.69$^{***}$ & 7.6$^{**}$ & 0 & 0.03$^{**}$ & 0\\
 & (2.36) & (2.33) & (2.94) & (0.01) & (0.01) & (0.01)\\
\textbf{Comparison Group:} &  &  &  &  &  & \\
All Nonprofits & $\checkmark$ &  &  & $\checkmark$ &  & \\
Nonprofits w/ MD &  & $\checkmark$ &  &  & $\checkmark$ & \\
\addlinespace
Nonprofits w/out MD &  &  & $\checkmark$ &  &  & $\checkmark$\\
Observations & 4945 & 1330 & 1815 & 12345 & 2895 & 4080\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:forprofit_uncompCMI_synth}Comparison to For-Profit Uncompensated Care and CMI Synthetic DiD Results}
\centering
\begin{tabular}[t]{l>{\centering\arraybackslash}p{.2textwidth}>{\centering\arraybackslash}p{.2textwidth}>{\centering\arraybackslash}p{.2textwidth}>{\centering\arraybackslash}p{.2textwidth}>{\centering\arraybackslash}p{.2textwidth}>{\centering\arraybackslash}p{.2textwidth}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Uncompensated Care} & \multicolumn{3}{c}{Case Mix Index} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7}
 & (1) & (2) & (3) & (1) & (2) & (3)\\
\midrule
For-Profit x Post Programs & 0.06$^{***}$ & 0.08$^{***}$ & 0.06$^{***}$ & 0 & 0.02$^{**}$ & 0\\
 & (0.01) & (0.01) & (0.01) & (0.01) & (0.01) & (0.01)\\
\textbf{Comparison Group:} &  &  &  &  &  & \\
All Nonprofits & $\checkmark$ &  &  & $\checkmark$ &  & \\
Nonprofits w/ MD &  & $\checkmark$ &  &  & $\checkmark$ & \\
\addlinespace
Nonprofits w/out MD &  &  & $\checkmark$ &  &  & $\checkmark$\\
 &  &  &  &  &  & \\
Observations & 4935 & 1330 & 1815 & 12320 & 2880 & 4065\\
\bottomrule
\multicolumn{7}{l}{\textsuperscript{} Results from Equation with readmission and mortality rates as outcome variables.}\\
\multicolumn{7}{l}{\textsuperscript{} Standard errors are clustered at the hospital level.}\\
\multicolumn{7}{l}{\textsuperscript{} Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1}\\
\multicolumn{7}{l}{\textsuperscript{} Uncompensated care measured as percent of total operating expenses.}\\
\end{tabular}
\end{table}
